Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-09-05 ms/main.tex
Another fix to result 3

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \alpha \frac{T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
	if \emph{(iii.a)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
	if \emph{(iii.b)} $T_A<T_B$ and $v<\hat v$ and $\hat\gamma_2 < c$.
\item \emph{Fixation of defection}: 
	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \alpha \frac{T}{1-T}$; or 
  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_1 < c$ and $\hat\gamma_2 < c$; or 
	if \emph{(vi)} $T_A<T_B$ and $\hat\gamma_1 < c$.
\item \emph{Stable Coexistence of both phenotypes at $\hat{p}^*$}: 
  if \emph{(vii.a)} $T_A < T_B$ and $v<\hat{v}$ and $\hat\gamma_1 < c < \hat\gamma_2$; or
  if \emph{(vii.b)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$. 
\item \emph{Unstable coexistence and fixation of either phenotype depending on initial frequency}:
  if \emph{(viii)}  $T_A>T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$.
\end{enumerate}

>>>>

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \alpha \frac{T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
	if \emph{(iii.a)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
	if \emph{(iii.b)} $T_A<T_B$ and $v<\hat v$ and $\hat\gamma_2 < c$.
\item \emph{Fixation of defection}: 
	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \alpha \frac{T}{1-T}$; or 
  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_2 < c$; or 
	if \emph{(vi)} $T_A<T_B$ and $\hat\gamma_1 < c$.
\item \emph{Stable Coexistence of both phenotypes at $\hat{p}^*$}: 
  if \emph{(vii.a)} $T_A < T_B$ and $v<\hat{v}$ and $\hat\gamma_1 < c < \hat\gamma_2$; or
  if \emph{(vii.b)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$. 
\item \emph{Unstable coexistence and fixation of either phenotype depending on initial frequency}:
  if \emph{(viii)}  $T_A>T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$.
\end{enumerate}
